Ecuador plant species BIEN occurrence cleaning

### 2023-03-23 code/L1/L1_NorthAndes_plants_BIEN_occ.Rmd

# Configure BIEN data to Darwin Core Standards
```{r}
# darwinizing a dataset
config <- read.csv(file.path(output_path,"configuration table.csv"))

>>>>

# Configure BIEN data to Darwin Core Standards
```{r}
# darwinizing a dataset
config <- read.csv(file.path(output_path,"Ecuador_plant_BIEN_occ_ConfigurationTable"))
